|

### 2021-02-22 manuscript/article.Rmd
change footnote placement

We employ two models to evaluate the effect of monetary incentives on dengue
incidence. The first is a differences-in-differences model that tests
whether the intervention _per se_ had any effect on dengue hospitalisations in
the city of Rio Verde. The second model compares dengue incidence in each of
the treatment statuses with incidence figures in the control group. The unit of
analysis is the census tract.\footnote{There were 139 Census Tracts analyzed by the 96 pairs. This because 43 pairs worked in more than one Census tract at once.} Table \ref{tab:incidence} displays the results
for our first model, in which we measure the impact of our intervention after 4,
8, 12, and 16 weeks. The last column shows how collective incentives compare
with individual bonuses, with the latter considered as the control group.

@@

In our second model, we measure the effect of reward schemes on the number of
hospitalisations per census tract. Table \ref{tab:census} shows hospitalisation
counts before the intervention, and then 15, 30, 60, 90, and between 30 to 60
days after the treatment.

>>>>

We employ two models to evaluate the effect of monetary incentives on dengue
incidence. The first is a differences-in-differences model that tests
whether the intervention _per se_ had any effect on dengue hospitalisations in
the city of Rio Verde. The second model compares dengue incidence in each of
the treatment statuses with incidence figures in the control group. The unit of
analysis is the census tract. Table \ref{tab:incidence} displays the results
for our first model, in which we measure the impact of our intervention after 4,
8, 12, and 16 weeks. The last column shows how collective incentives compare
with individual bonuses, with the latter considered as the control group.

@@

In our second model, we measure the effect of reward schemes on the number of
hospitalisations per census tract. Table \ref{tab:census} shows hospitalisation
counts before the intervention, and then 15, 30, 60, 90, and between 30 to 60
days after the treatment.\footnote{There were 139 Census Tracts analyzed by the 96 pairs. This because 43 pairs worked in more than one Census tract at once.}
